Appendix to 'cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-22 jss/appendix.Rmd
knitted appendix

Figure XXX in this section can also be made using \pkg{cubble} and \pkg{leaflet}, in which case the temperature range is displayed as a small subplot upon clicking on the map. This procedure involves first creating the popup plots from the long form cubble as a vector and then adding these plots to a leaflet map created from the nested cubble, with \code{leafpop::addPopupGraphs()}:

>>>>

Figure XXX in this section can also be made using `cubble` and `leaflet`, in which case the temperature range is displayed as a small subplot upon clicking on the map. This procedure involves first creating the popup plots from the long form cubble as a vector and then adding these plots to a leaflet map created from the nested cubble, with \code{leafpop::addPopupGraphs()}:
